---
title: "Report"
output: html_document
---

## Data analysis

First we load the training data set.
```{r dataread, cache=TRUE}
training <- read.csv("pml-training.csv")
```

Than we do some other general setup.
```{r}
library <- function(...) {suppressMessages(base::library(...))}
```

We restrict our attention only to complete sensor variables

```{r}
select <- names(which(sapply(training[8:159], function(c) { 
    if (class(c) == 'factor') return(F);
    if (any(is.na(c))) return(F);
    return(T);
    })))
```

We use a randomForest model on the selected variables

```{r}
library(randomForest)
fitmodel <- function(df) {
    mod <- randomForest(df[,select],df[,160])
    function(nd) { predict(mod, nd[,select])}
}

```

Cross-validation
----------------

We set up k-fold cross-validation.
```{r foldedmodels, cache=TRUE}
library(caret)
set.seed(45681)
folds <- createFolds(training$classe, k=5, returnTrain = T)
models <- lapply(folds, function(f) fitmodel(training[f,]))
```

Then we can assess the out-of-sample error rate on each fold:

```{r errorstats, cache=TRUE}
error.rate <- function(mod, df) {
    sum(mod(df)!=df[,160])/nrow(df)
}

error.rates <- sapply(1:length(folds), function(i) error.rate(models[[i]], training[-folds[[i]],]))
summary(error.rates)
print(mean.error.rate <- mean(error.rates))
```

Based on these results the out-of-sample error rate is expected to be `r mean.error.rate`.

## Full Model

We can then train the model on the full training data set

```{r fullmodel, cache=TRUE}
full <- fitmodel(training)
```

## Testing

Finally, we load the testing dataset and apply the full model.

```{r testing, cache=TRUE}
testing <- read.csv("pml-testing.csv")

print(answers <- full(testing))
```

Then, we save the results into separate files for submission.
 
```{r}
pml_write_files <- function(answers, folder){
    dir.create(folder, showWarnings=FALSE)
    for(i in 1:length(answers)) {
        write.table(
            answers[i],file=file.path(folder, sprintf("problem_id_%02d.txt", i)),
            quote=FALSE,row.names=FALSE,col.names=FALSE)
    }
}

pml_write_files(answers, "output")
```

